Type-Safe Modular Parsing

### 2017-09-05 SLE_17/paper.tex
shortening.
Change code font size.

\lstset{
  language=JavaScala,                % choose the language of the code
  columns=flexible,
  lineskip=-1pt,
  basicstyle=\ttfamily\small,       % the size of the fonts that are used for the code
  numbers=none,                   % where to put the line-numbers
  numberstyle=\ttfamily\tiny,      % the size of the fonts that are used for the line-numbers
  stepnumber=1,                   % the step between two line-numbers. If it's 1 each line will be numbered
  numbersep=5pt,                  % how far the line-numbers are from the code
  backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
  showspaces=false,               % show spaces adding particular underscores
  showstringspaces=false,         % underline spaces within strings
  showtabs=false,                 % show tabs within strings adding particular underscores
  morekeywords={var, lazy},
  %  frame=single,                   % adds a frame around the code
  tabsize=2,                  % sets default tabsize to 2 spaces
  captionpos=none,                   % sets the caption-position to bottom
  breaklines=true,                % sets automatic line breaking
  breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
  title=\lstname,                 % show the filename of files included with \lstinputlisting; also try caption instead of title
  escapeinside={(**}{**)},          % if you want to add a comment within your code
  keywordstyle=\ttfamily\bfseries,
}

@@

%% Keywords
%% comma separated list
\keywords{modular parsing, object algebras, semantic modularity}  %% \keywords is optional

@@

\section*{Acknowledgements}
We would like to thank the anonymous reviewers for their helpful comments. This work has been sponsored by the Hong Kong Research Grant Council projects number 27200514 and 17258816.

>>>>

\lstset{
  language=JavaScala,                % choose the language of the code
  columns=flexible,
  lineskip=-1pt,
  basicstyle=\ttfamily\footnotesize,       % the size of the fonts that are used for the code
  numbers=none,                   % where to put the line-numbers
  numberstyle=\ttfamily\tiny,      % the size of the fonts that are used for the line-numbers
  stepnumber=1,                   % the step between two line-numbers. If it's 1 each line will be numbered
  numbersep=5pt,                  % how far the line-numbers are from the code
  backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
  showspaces=false,               % show spaces adding particular underscores
  showstringspaces=false,         % underline spaces within strings
  showtabs=false,                 % show tabs within strings adding particular underscores
  morekeywords={var, lazy},
  %  frame=single,                   % adds a frame around the code
  tabsize=2,                  % sets default tabsize to 2 spaces
  captionpos=none,                   % sets the caption-position to bottom
  breaklines=true,                % sets automatic line breaking
  breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
  title=\lstname,                 % show the filename of files included with \lstinputlisting; also try caption instead of title
  escapeinside={(**}{**)},          % if you want to add a comment within your code
  keywordstyle=\ttfamily\bfseries,
}

@@

%% Keywords
%% comma separated list
\keywords{modular parsing, Object Algebras, semantic modularity}  %% \keywords is optional

@@

\vspace{-6pt}
\section*{Acknowledgements}
We would like to thank the anonymous reviewers for their helpful comments. This work has been sponsored by the Hong Kong Research Grant Council projects number 27200514 and 17258816.
\vspace{-6pt}
